Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-18 paper.tex
blocking (rewrite, wip)

In this work, author disambiguation is cast into a semi-supervised clustering
problem, as inspired from several previous works described in Section~\ref
{related-works}. Our algorithm is made of three elements: (i) a blocking
function $b$ whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
reduce computational complexity; (ii) the construction of a similarity function
$d$ between signatures using supervised learning; (iii) the
semi-supervised clustering of all signatures within a same block, using $d$ as a pseudo distance metric.

@@

@@

\subsection{Semi-supervised clustering}
% hierarchical clustering
% semi-supervised clustering
% cold start problem (when no labels in a block)

>>>>

As inspired from several previous works described in Section~\ref{related-works},
we cast in this work author disambiguation into a semi-supervised clustering
problem.  Our algorithm is made of three parts: (i) a blocking
scheme whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
reduce computational complexity; (ii) the construction of a similarity function
$d$ between signatures using supervised learning; (iii) the
semi-supervised clustering of all signatures within a same block, using $d$ as a pseudo distance metric.

@@

\subsection{Blocking}
\label{methods:blocking}

As in previous works, the first part of our algorithm consists in grouping
signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, and then to carry out
author disambiguation independently on each one of these blocks. In doing so,
computational complexity of clustering (see Section~\ref{methods:clustering})
typically reduces from $O(S^2)$ to $O(\sum_b S_b^2)$, which becomes much more
tractable as the number of signatures increases. Since disambiguation is
performed independently per block, a good blocking strategy should also be
designed such that signatures from the same author are all mapped to the same
block, otherwise directly preventing their correct clustering in later stages. As a
result, blocking should balance between reduced complexity and maximum recall.

The simplest and most common strategy for blocking \glnote{add references}
groups signatures together if they share the same surname(s) and the same first
given name initial (e.g., "Doe, J").

\vspace{3cm}

@@

\subsection{Semi-supervised clustering}
\label{methods:clustering}

% hierarchical clustering
% semi-supervised clustering
% cold start problem (when no labels in a block)
